### 2008-10-22 trunk/Latex/H2Preview/H2PrevSummary.tex
DJNL written conclusions

Discrete-time preview controllers are composed of a high-order Finite Impulse Response (FIR) preview component, and low-order Infinite Impulse Response (IIR) components. This structure is illustrated in Figure~\ref{fig:PrevContStruct}, and is also highlighted in the continuous-time case in \cite{Moelja_2006_H2PreviewMultiple}. A proof is provided for the discrete-time case in Section \ref{sec:H2OF}. If the controller is written in observer form, then the states of the FIR preview block and the order $n_r$ IIR block are (perfect) reconstructions of the states of $\Phi$ and $W_r$ respectively. The state of the order $n_g$ IIR block is an estimate for the state of $G$.

@@

\end{figure}}
\item[The optimal control is independent of $W_r$ for large $N$]
This phenomenon was first noticed in \cite{Tomizuka_1975_OptDiscretePreview}, with a proof provided in Section \ref{sec:H2FI}. It is instructive to consider the influence of $W_r$ from a stochastic perspective. Since $\eta$ is assumed to be a realisation of a white-noise process, then a dynamic $W_r$ provides statistical information on future values of $r$. If, for example, $W_r$ is low-pass, the $r(k)$'s will become correlated and hence $W_r$ will introduce `statistical preview' beyond the preview horizon. We would therefore expect $W_r$ to reduce the need for preview, and also that its influence on the control would decline as $N$ tends to infinity.

@@

\begin{description}
\item[Preview improves steady-state disturbance rejection.] 
Figure~\ref{fig:BetterSSWithIncN} illustrates the `non-responsiveness' of the closed-loop system in the case of no reference weight, and a low preview horizon. The system's response improves as the preview horizon is extended; this effect can also be seen in the control signal.

@@

Consider the full-information controller synthesis problem illustrated in Figure~\ref{fig:PrevTrackSysFI} and let $W_e$ be a dynamic
tracking-error filter. A low-pass weight on the tracking error improves the steady-state tracking performance, without changing the assumed frequency content of the reference signal. If $W_r=1$, $r$ is assumed to be a realization of a white-noise process. However, the inclusion of a low-pass tracking-error filter ($W_e$) ensures that the low-frequency components of $r$ will be tracked accurately, in contrast to Figure~\ref{fig:BetterSSWithIncN}. This is accomplished via feedback based on the states of $W_e$, which is low-pass and so there is no initial `spike' in the control signal. 

@@

\item[Integral action with output feedback.]
An output-feedback tracking controller with integral action is described by Figure \ref{fig:TrackSysInteg}, which also serves to
illustrate the complexity of problems that may be tackled  using the framework in Figure 1.
A measurement of the integrated error signal is required in order to ensure that the tracking-error integrator state is  detectable. 
Tuning the relative magnitudes of $W_{e1}$ and $W_{e2}$ is akin to adjusting the gains in a PI controller. The ability to adjust the integral gain is useful, because too much integral action can be detrimental to stability and/or the transient response.

@@

\psfrag{W_e1}{$W_{e1}$}
\psfrag{W_e2}{$W_{e2}$}
\psfrag{W_n}{$W_{n}$}
\psfrag{z3}{$z_3$}
\psfrag{y1}{$y_1$}
\psfrag{y2}{$y_2$}
\psfrag{I1/(z-1)}{$I\frac{1}{\z-1}$}
\includegraphics[width=12cm]{./diags/TrackSysInteg.eps}
\caption{Preview tracking with integral action. The signal $z=\left[z_1'\,\,z_2'\,\,z_3'\right]'$ is the output of the closed-loop transfer function
whose 2-norm is to be minimised; $y=\left[y_1'\,\,y_2'\right]'$ is the measurement signal. The transfer functions $W_{e1}$, $W_{e2}$ and $W_n$ are shaping filters. Other notation follows that of Figure \ref{fig:DistRejSys}. \label{fig:TrackSysInteg}}

>>>>

Discrete-time preview controllers are composed of a high-order Finite Impulse Response (FIR) preview component, and low-order {IIR} components. This structure is illustrated in Figure~\ref{fig:PrevContStruct}, and is also highlighted in the continuous-time case in \cite{Moelja_2006_H2PreviewMultiple}. A proof is provided for the discrete-time case in Section \ref{sec:H2OF}. If the controller is written in observer form, then the states of the FIR preview block and the order $n_r$ IIR block are (perfect) reconstructions of the states of $\Phi$ and $W_r$ respectively. The state of the order $n_g$ IIR block is an estimate for the state of $G$.

@@

\end{figure}}\item[The optimal control is independent of $W_r$ for large $N$]
This phenomenon was first noticed in \cite{Tomizuka_1975_OptDiscretePreview}, with a proof provided in Section \ref{sec:H2FI}. It is instructive to consider the influence of $W_r$ from a stochastic perspective. Since $\eta$ is assumed to be a realisation of a white-noise process, then a dynamic $W_r$ provides statistical information on future values of $r$. If, for example, $W_r$ is low-pass, the $r(k)$'s become correlated and hence $W_r$ introduces `statistical preview' beyond the preview horizon. We would therefore expect $W_r$ to reduce the need for preview, and also that its influence on the control would decline as $N$ tends to infinity.

@@

The discrete transfer function $\hat G$ was obtained by discretising
\als{       \frac{101}{s (s^2 + 2s + 101)},}
using a sample time of 0.001 seconds.
We search for a $K$ which minimises $\nrm{T_{\eta\rightarrow z}}_{2,\infty}$, or equivalently, the $K$ which minimises:
\aln{
\nrm{\ma{W_eW_rT_{r\rightarrow e}\\W_rT_{r\rightarrow u}}}_{2,\infty} \label{eqn:DesInsightCL}
.}
Clearly this represents a tracking problem in which minimisation of tracking errors must be balanced against  excessive control requirements. The transfer functions $W_r$ and $W_e$ may be chosen to reflect, respectively, the expected frequency content of $r$, and the importance of achieving good tracking at a given frequency. We will now use this example to illustrate some general properties of $\htwo$ preview tracking controllers.

\begin{description}
\item[Preview improves steady-state tracking.] 
Figure~\ref{fig:BetterSSWithIncN} illustrates the `non-responsiveness' of the closed-loop system in the case of no reference weight, and a low preview horizon. In the limiting case, where there is zero preview and no reference weighting, the controller does not have any information about the value of the reference at the next time step, and so it cannot make a decision about the direction in which to send the plant. Therefore, the tracking error cost cannot be reduced, and so the optimal controller can only minimise the control cost, leading to a choice of $u=0$.

Alternatively, as $N\rightarrow \infty$, then the steady state error tends towards zero (in the absence of disturbances or modelling errors). 

@@

Consider the Full Information controller synthesis problem illustrated in Figure~\ref{fig:PrevTrackSysFI} and let $W_e$ be a dynamic
tracking-error filter. A low-pass weight on the tracking error improves the low-frequency tracking performance, without needing to change the assumed frequency content of the reference signal (i.e. without changing $W_r$). Note that a step change in the reference does not lead to a `spike' in the control signal -- see Figure \ref{fig:ReducingControlWithIncreasingN}. 

@@

\item[Preview only improves low frequency tracking performance.] For a low-pass plant, high frequency tracking performance is limited by the prohibitive amplitude of the control action. This is a fundamental feature of the plant and cannot be changed by anticipative action. This effect is illustrated in Figure~\ref{fig:sigmah2}, where preview improves the low-frequency performance by reducing the magnitude of both the tracking error and the control signal. %The price for this improvement appears to be larger control action at higher frequencies

@@

\subfloat[Unweighted plant]{\includegraphics[width=\columnwidth]{./diags/UnweightedSigmaH2.eps}}

\subfloat[$W_e=\frac{1}{\z-1}$]{\includegraphics[width=\columnwidth]{./diags/WeightedSigmaH2.eps}}
\caption{Bode plots of the closed-loop transfer functions $T_{r\rightarrow e}$ and $T_{r\rightarrow u}$ which result from application of the $\hinf$-optimal controls.\label{fig:sigmah2} The unweighted plant is considered in (a), and a low-pass $W_e$ is employed in (b).}
\end{figure}
\item[Integral action with output feedback.]
An output-feedback tracking controller with integral action is described by Figure \ref{fig:TrackSysIntegDesign}, which also serves to
illustrate the complexity of problems that may be tackled  using the framework in Figure 1. Note that the integrated error signal must be included in the measurements in order to ensure that the integrator state is detectable.

Tuning the relative magnitudes of $W_{e1}$ and $W_{e2}$ is akin to adjusting the gains in a PI controller. %The ability to adjust the integral gain is useful, because too much integral action can be detrimental to stability and/or the transient response. 
In fact a `derivative' signal could also be added, thus completing the PID analogy and facilitating tuning of the preview controller.

Previously, the addition of integral action has been approached in an {LQG} setting through the use of the differentiated control signal in the cost function \citep[e.g. ][]{Tomizuka_1979_IntegralPreviewFI,Katayama_1987_PreviewAndIntegral,Tomi_1980_FFPrev}. Such an approach does not allow one to adjust the strength of the integral action, which is likely to lead to difficulty in satisfying stability/performance requirements.

\begin{figure}
\begin{center}
\stdcontrolfrags
\psfrag{W_e1}{$W_{e1}$}
\psfrag{W_e2}{$W_{e2}$}
\psfrag{W_n}{$W_{n}$}
\psfrag{z1}{$z_1$}
\psfrag{z2}{$z_2$}
\psfrag{z3}{$z_3$}
\psfrag{y1}{$y_1$}
\psfrag{y2}{$y_2$}
\psfrag{I1/(z-1)}{$I\frac{1}{\z-1}$}
\includegraphics[width=12cm]{./diags/TrackSysInteg.eps}
\end{center}
\caption{Preview tracking with integral action. The signal $z=\left[z_1'\,\,z_2'\,\,z_3'\right]'$ is the output of the closed-loop transfer function
whose 2-norm is to be minimised; $y=\left[y_1'\,\,y_2'\right]'$ is the measurement signal. The transfer functions $W_{e1}$, $W_{e2}$ and $W_n$ are shaping filters. Other notation follows that of Figure \ref{fig:DistRejSys}. \label{fig:TrackSysIntegDesign}}
\end{figure}
